Preliminary insights into the use of pottery and culinary practices at Guijiabao site in southwest China

### 2024-05-26 analysis/paper/paper.Rmd
updated the repository for data

The data generated by these analyses and R code used for visualizations are openly available at https://github.com/LiYingWang/GJBpottery for research reproducibility and transparency [@Marwick2017; @MarwickandWang2022].

>>>>

The data generated by these analyses and R code used for visualizations are openly available at https://osf.io/46bpf/ for research reproducibility and transparency [@Marwick2017; @MarwickandWang2022].
